Hypertension and microbiome

### 2019-01-03 rrbiome.Rmd
Minor

```{r maaslin scatter plot, fig.width = 10, fig.height = 20, dpi = 300}
ggplot(df.merged %>% gather(Covariate, relabundance, maas.signf.features), aes(x = asin(sqrt(relabundance)), y = SYSTM, color = SEX)) +
    facet_wrap(~Covariate, ncol=2, scales = "free") +
    geom_point(size = 0.2) +
    scale_y_continuous(breaks=seq(0,200,40)) +
    geom_smooth(method=lm, se=TRUE, size=0.5) +
    stat_poly_eq(formula = "y ~ x",
                 aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
                 label.y.npc = "bottom",
                 parse = TRUE,
                 size = 3) +   
    ggplot2::theme_minimal() 
```

>>>>

```{r maaslin scatter plot, fig.width = 10, fig.height = 20, dpi = 300}
ggplot(df.merged %>% gather(Covariate, relabundance, maas.signf.features), aes(x = asin(sqrt(relabundance)), y = SYSTM, color = SEX)) +
    facet_wrap(~Covariate, ncol=2, scales = "free") +
    geom_point(size = 0.2) +
    scale_y_continuous(breaks=seq(0,200,40)) +
    geom_smooth(method=lm, se=TRUE, size=0.5) +
    stat_poly_eq(formula = "y ~ x",
                 aes(label = paste(..eq.label.., ..rr.label.., sep = "~~~")),
                 label.y.npc = "bottom",
                 label.x.npc = "right",
                 parse = TRUE,
                 size = 3) +   
    ggplot2::theme_minimal() 
```
